\documentclass{article}

\usepackage{array}
\usepackage{amsmath}
\usepackage{enumitem}

\begin{document}

\title{MANU 130 Mill Test Process Plan}
\author{John Bush}

\maketitle

\section*{Rough Stock}
\begin{enumerate}
	\item Select $2"$ square Aluminum bar.
\end{enumerate}

\section*{Bandsaw}
\begin{enumerate}[resume]
	\item Cut bar to length $3.125"$.
\end{enumerate}

\section*{Vertical Mill}
\begin{enumerate}[resume]
	\item Set in vise with $1 \frac{1}{2}"$ parallels.

	\item Face top of material with 4-flute, $\frac{3}{4}"$ end mill.  Spindle speed should be 3000 RPM, feed rate 60 IPM.

	\item Face reference sides with endmill.

	\item Mill remaining sides to final dimensions.  Length is $3.000" \pm 0.011"$.  Width is $1.875" \pm 0.009"$.

	\item Drill center hole with U twist drill bit.  Drill at 2000 RPM.  Center hole is centered $1.500"$ from edge along length, $0.938"$ from edge along width.

	\item Countersink center hole.  Use $90^\circ$ countersink bit to depth $0.066"$ for final countersink radius $\phi = 0.500"$.  Countersink speed should not exceed 400 RPM.

	\item Tap center hole 7/16-14 UNC - 1B to depth $1.000"$. (14 turns)

	\item Drill first corner hole ($0.375"$ from edges of reference corner) with $\frac{13}{32}"$ twist drill.  Drill at 2000 RPM.

	\item Counterbore corner hole with $\phi = 0.625"$ counterbore to depth $0.406"$.  Counterbore speed should not exceed 650 RPM.

	\item Drill and counterbore remaining corner holes.  Corner hole centers are $2.250"$ apart along axis of length and $1.125"$ apart along axis of width.

	\item Reverse workpiece in vise to prepare bottom surface.  Mill bottom to final dimension.  ($1.500" \pm 0.007"$)

	\item Deburr as needed.
\end{enumerate}

\newpage

\begin{table}[ht]
\centering
\caption{Inspection Report}
\renewcommand\arraystretch{3}
\begin{tabular}{l | m{2cm} | m{2cm} | m{2cm} | m{2cm} | m{2cm} |}
	Dimension & Value($"$) & Max($"$) & Min($"$) & Actual($"$) & In Tol? \\
	\hline
	Length & 3.000 & 3.011 & 2.989 && \\
	\hline
	Width & 1.875 & 1.884 & 1.866 && \\
	\hline
	Height & 1.500 & 1.507 & 1.493 && \\
	\hline
\end{tabular}
\end{table}
\end{document}

